Fixing Vulnerabilities Hinders Maintainability

### 2019-02-04 paper/ICPC19/icpc19.tex
median of differences is zero

\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.56\textwidth]{figures/language.pdf}
 	\caption{Maintainability difference by language after security refactorings}
	\label{fig:lang_main}
\end{figure}

@@

\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.57\textwidth]{figures/category.pdf}
 	\caption{Maintainability difference by pattern after security refactorings}
	\label{fig:pat}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=0.56\textwidth]{figures/language.pdf}
  \caption{Maintainability difference by language after security refactorings.}
  \label{fig:lang_main}
\end{figure}

@@

\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.57\textwidth]{figures/category.pdf}
 	\caption{Maintainability difference by pattern after security refactorings.
  \Luis{a median e' zero em muitos casos -- como interpretam isso? se nao houver
boa/simples explicacao talvez seja melhor usar o common language.}}
	\label{fig:pat}
\end{figure}
